Biology background

### 2014-12-03 Rmarkdown/biology_background.Rmd
Minor fixes
Added TODO re CHARM

@@

Some examples of these targeted bisulfite-sequencing are:
- Reduced representation bisulfite-sequencing (_RRBS_, \cite{Meissner:2005eb}): RRBS uses restriction enzymes to first select regions of the genome with a high CpG density (based on the Msp-I cleavage motif), which are subsequently treated with sodium-bisulfite and sequenced.
- NimbleGen's SeqCap Epi Enrichment System and Agilent's SureSelectxt Human Methyl-Seq: Both of these commercial products use DNA hybridisation to enrich the sequencing library for pre-defined regions of interest. This enriched library is then bisulfite-converted and sequenced.

>>>>

__TODO: Describe CHARM \citep{Irizarry:2008hg}, although not yet sure which sub-section it should appear in__.

@@

Some examples of these targeted bisulfite-sequencing are:
- Reduced representation bisulfite-sequencing (_RRBS_, \cite{Meissner:2005eb}): RRBS uses restriction enzymes to first select regions of the genome with a high CpG density (based on the Msp-I cleavage motif), which are subsequently treated with sodium-bisulfite and sequenced.
- Extended reduced representation bisulfite-sequencing, also known as enhanced reduced representation bisulfite-sequencing (eRRBS, \cite{Akalin:2012he}). A modified version of the RRBS protocol.
- NimbleGen's SeqCap Epi Enrichment System and Agilent's SureSelectxt Human Methyl-Seq: Both of these commercial products use DNA hybridisation to enrich the sequencing library for pre-defined regions of interest. This enriched library is then bisulfite-converted and sequenced.
